Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Include different types of AR in shiny app

### Adding not taken courses
```{r}
d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
  left_join(d_transactions, by = c("sequenceID","item")) %>%
  mutate(
    Taken= case_when(
     is.na(Grade)  ~ "not taken",
      T             ~ "taken"),
    item_Taken= paste(item,Taken, sep = "_")
     )

#ARRANGE PROPERLY

d_transactions <- d_transactions_tmp

rm(d_transactions_tmp)
```

@@

#
# Making transactions
transactions       <- make_transaction(item = item   )
transactions_PF    <- make_transaction(item = item_PF)
transactions_HL    <- make_transaction(item = item_HL)
transactions_Taken <- make_transaction(item=item_Taken)

@@

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken,
     file = "App/ARR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR, AR_PF, AR_HL, AR_Taken)

>>>>

### Adding not taken courses
```{r}
d_transactions_not_taken <- expand.grid(

  # Expand along students (sequenceID) and courses (itemID)
  sequenceID = unique(d_transactions$sequenceID),
  item       = unique(d_transactions$item),
  stringsAsFactors = FALSE
  ) %>%

  # Join with d_transactions
  left_join(
    d_transactions, 
    by = c("sequenceID", "item")
    ) %>%

  # Create 
  mutate(

    taken = case_when(
      is.na(Grade) ~ "not taken",
      TRUE         ~ "taken"),

    item_taken= paste(item, taken, sep = "_")

     )

@@

#
# Making transactions
transactions       <- make_transaction(item = item   )
transactions_PF    <- make_transaction(item = item_PF)
transactions_HL    <- make_transaction(item = item_HL)
transactions_Taken <- make_transaction(data = d_transactions_not_taken, item = item_taken)

@@

#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken,
     file = "App/AR.RDATA")

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken)
